{{< var titll >}}

### 2024-07-13 addendum/Addendum_az.qmd
abcdef

---
title: "Addendum"
subtitle: "Arizona General Election 2022"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

>>>>

---
title: "{{< var addns >}}"
subtitle: "{{< var addnl >}}"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
execute: 
  cache: false
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
output: 
  html_document:
    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
nocite: |
  @*
---

### 2024-07-13 addendum/Addendum_ne.qmd
abcdef

---
title: "Addendum"
subtitle: "Nevada General Election 2022"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

>>>>

---
title: "{{< var addas >}}"
subtitle: "{{< var addal >}}"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
execute: 
  cache: false
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
output: 
  html_document:
    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
nocite: |
  @*
---

### 2024-07-13 presentation.qmd
abcdef

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
modlat <- eqpar$meql
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
appnf <- seloutput(rppnf <- selreport(basc))
appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
#round(polynom::integral(penf,c(0,1)),3)
```

>>>>

```{r}
knitr::knit_exit()
```

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
appnf <- seloutput(rppnf <- selreport(basc))
appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
```

```{r}
knitr::knit_exit()
```
